\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-27 paper/experiments.tex
Add fcc acronym at first appearance

\subsubsection{freeCodeCamp 2016 New Coder Survey}
For our second set of experiments, we chose to use data collected
by freeCodeCamp as a part of a survey of new software developers
(both professional and amateur)~\cite{fcc-data}. freeCodeCamp is an open-source
community that helps users learn how to program. Their \textit{2016 New Coder Survey} consists of responses by over 15,000 people to 48 different
demographic and programming-related questions.
The survey targeted users who were related to coding organizations.

>>>>

\subsubsection{freeCodeCamp 2016 New Coder Survey}
For our second set of experiments, we chose to use data collected
by freeCodeCamp (FCC) as a part of a survey of new software developers
(both professional and amateur)~\cite{fcc-data}. freeCodeCamp is an open-source
community that helps users learn how to program. Their \textit{2016 New Coder Survey} consists of responses by over 15,000 people to 48 different
demographic and programming-related questions.
The survey targeted users who were related to coding organizations.
